\documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage{fontawesome5}
\usepackage[usenames,dvipsnames]{xcolor} % Fixed: Combined color packages
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[colorlinks=true, urlcolor=NavyBlue]{hyperref} % Fixed: visible colored links
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}

% Font configuration
\RequirePackage{iftex}
\ifpdftex
  \usepackage[T1]{fontenc}
\fi
\usepackage{charter}

\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\setlength{\footskip}{5pt}

% Adjust margins
% Adjust margins
\usepackage[margin=0.5in]{geometry}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-2pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-2pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1.5pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \vspace{-1.5pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-4pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Md. Abdur Rahim} \\ \vspace{2pt}
    \small \faPhone \ +88015-37274080 $|$ \faEnvelope \ \href{mailto:rahim.cse.diu@gmail.com}{rahim.cse.diu@gmail.com} $|$ 
    \faLinkedin \ \href{https://www.linkedin.com/in/foundyourahim/}{linkedin.com/in/foundyourahim} $|$
    \faGithub \ \href{https://github.com/rahim-jr}{github.com/rahim-jr}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Daffodil International University}{Ashulia, Dhaka, Bangladesh}
      {Bachelor of Science in Computer Science \& Engineering}{Aug. 2021 -- May 2025}
      \resumeItemListStart
        \resumeItem{Relevant Coursework: Data Structures, Algorithms, Software Engineering, Database Systems.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: C/C++, Python, JavaScript, TypeScript, Golang} \\
     \textbf{Frontend}{: React.js, Next.js, Tailwind CSS, Radix UI, Figma} \\
     \textbf{Backend}{: Node.js, Express.js, RESTful APIs, JWT, OAuth} \\
     \textbf{Database \& Tools}{: PostgreSQL, MongoDB, Prisma, Docker, Git/GitHub, Postman}
    }}
 \end{itemize}

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
        \resumeProjectHeading
          {\textbf{\href{https://github.com/rahim-jr/job-board-ts}{\faGithub \ Job Board SaaS Platform}} $|$ \emph{Next.js, TypeScript, Prisma, PostgreSQL, Stripe}}{2025}
          \resumeItemListStart
            \resumeItem{Engineered a scalable Job Board SaaS platform using \textbf{Next.js}, supporting distinct employer/candidate workflows with \textbf{rich-text editors} and optimized \textbf{server-side filtering}.}
            \resumeItem{Integrated \textbf{Stripe} for secure payments and \textbf{UploadThing} for efficient media handling, enabling seamless monetization features.}
            \resumeItem{Implemented \textbf{Server Actions} and \textbf{Inngest} to handle asynchronous background jobs, ensuring reliable data processing.}
            \resumeItem{Architected a normalized \textbf{Prisma} schema to manage complex relationships between users, jobs, and applications.}
            \resumeItem{Enhanced performance using \textbf{Next.js Image optimization}, dynamic imports, and strategic \textbf{caching}, significantly reducing load times.}
            \resumeItem{Deployed on \textbf{Vercel} with automated CI/CD pipelines to ensure code quality and rapid delivery.}
          \resumeItemListEnd

        \resumeProjectHeading
          {\textbf{\href{https://github.com/rahim-jr/fintech-api}{\faGithub \ Secure Fintech Wallet}} $|$ \emph{TypeScript, Express, PostgreSQL (Docker), Jest, Prisma}}{2024}
          \resumeItemListStart
            \resumeItem{Engineered a secure Fintech backend with \textbf{Optimistic Concurrency Control}, effectively preventing double-spending in high-load environments.}
            \resumeItem{Attained \textbf{95\% test coverage} using \textbf{Jest} and \textbf{Supertest}, ensuring robust system reliability and zero regression.}
            \resumeItem{Designed and documented a RESTful API using \textbf{Swagger/OpenAPI} for seamless third-party integration.}
            \resumeItem{Strengthened security with \textbf{JWT} authentication, \textbf{Zod} validation, and input sanitization to prevent common vulnerabilities.}
          \resumeItemListEnd

        \resumeProjectHeading
          {\textbf{\href{https://github.com/rahim-jr/react-weather-app}{\faGithub \ React Weather Forecast Application}} $|$ \emph{React, JS, CSS, OpenWeatherMap API}}{2023}
          \resumeItemListStart
            \resumeItem{Built a responsive weather dashboard using \textbf{React}, integrating \textbf{OpenWeatherMap API} for real-time forecasts.}
            \resumeItem{Implemented \textbf{dynamic icons} and interactive search to enhance user engagement and visual appeal.}
            \resumeItem{Deployed to \textbf{Netlify} with a component-based architecture for maintainability and speed.}
          \resumeItemListEnd

        \resumeProjectHeading
          {\textbf{\href{https://github.com/rahim-jr/Amazon-lite-ecommerce-lite}{\faGithub \ E-commerce API}} $|$ \emph{Node.js, TypeScript, Express, MongoDB}} {2025 -- Present}
          \resumeItemListStart
            \resumeItem{Developing a robust E-commerce API with \textbf{Node.js} and \textbf{TypeScript}, featuring secure \textbf{JWT authentication} and access control.}
            \resumeItem{Designing \textbf{RESTful endpoints} for scalable user management and order processing.}
            \resumeItem{Utilizing \textbf{Mongoose ODM} for efficient data modeling and secure session management.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------ACHIEVEMENTS-----------
\section{Achievements \& Leadership}
    \resumeSubHeadingListStart
        \resumeProjectHeading
            {\textbf{ICPC Participant} $|$ \emph{ACM International Collegiate Programming Contest}}{2022, 2023}
            \resumeItemListStart
              \resumeItem{Participated in ICPC Preliminary rounds for two consecutive years}
            \resumeItemListEnd
        \resumeProjectHeading
            {\textbf{Second Runner Up} $|$ \emph{\href{https://toph.co/c/diu-take-off-2022/standings}{DIU Take-off Programming Contest}}}{Spring, 2022}
            \resumeItemListStart
              \resumeItem{Secured 3rd position in competitive programming contest among 500+ participants, hosted in 2 rounds.}
            \resumeItemListEnd
        \resumeProjectHeading
            {\textbf{ACM Executive} $|$ \emph{Daffodil International University}}{2021-2022}
            \resumeItemListStart
              \resumeItem{Organized programming contests and technical events for university students and computer science community}
              \resumeItem{Enhanced student engagement through collaborative initiatives with faculty and effective communication}
            \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------PROBLEM SOLVING-----------
\section{Problem Solving}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Competitive Programming} $|$ \emph{650+ Problems Solved}}{2020 -- Present}
          \resumeItemListStart
            \resumeItem{Solved \textbf{650+ problems} on Codeforces, LeetCode, HackerRank, CodeChef focusing on algorithms and data structures.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

\end{document}